### 2022-02-15 ack.tex
typos

Last but not the least, I would like to thank Dragana for being always there on my side, for being so kind and patient, and for her help in putting the ideas of this thesis into text.
You are the best.

>>>>

Last but not the least, I would like to thank Dragana for being always there by my side, for being so kind and patient, and for her help in putting the ideas of this thesis into text.
You are the best.
